Exploring Local Explanations of Nonlinear Models Using Animated Linear Projections

### 2022-02-06 _paper.rmd
figure 3, labeling consistency, caption touch up

```{r regressioncase, echo=F, out.width="100%", fig.cap="Overview of the cheem viewer for regression task highlighting the differences from the classification task and interactive features. Panel (a) shows linked brushing across the global view and the tooltip display when the cursor hovers over an instance. Applied linked brushing, (b), selected points are highlighted in the component spaces and tabularly displayed. Coloring on a statistic (c) highlights structure organized in the attribution space. Interactive tabular display (d) populates when instances are selected. Contribution of the 1D basis effecting the horizontal position (e) parallel coorindate display of the feature attribution from all observations, and horizontal bars show the contribution to the current basis. Regression projection (f) uses the same horizontal projection and fixes the vertical positions to the observed y and residuals, (left and right)."}
knitr::include_graphics("./figures/app_regression_interactions.PNG")
```

>>>>

```{r regressioncase, echo=F, out.width="100%", fig.cap="Overview of the cheem viewer for regression task highlighting the differences from the classification task and interactive features. Panel (a) PCA of the data and attributions spaces, (b), residual plot, predictions by observed values. Four points areselected points and highlighted in the PC spaces and tabularly displayed. Coloring on a statistic (c) highlights structure organized in the attribution space. Interactive tabular display (d) populates when instances are selected. Contribution of the 1D basis effecting the horizontal position (e) parallel coorindate display of the feature attribution from all observations, and horizontal bars show the contribution to the current basis. Regression projection (f) uses the same horizontal projection and fixes the vertical positions to the observed y and residuals, (left and right)."}
knitr::include_graphics("./figures/app_regression_interactions.PNG")
```

### 2022-02-06 _paper.tex
figure 3, labeling consistency, caption touch up

\caption{Overview of the cheem viewer for regression task highlighting the differences from the classification task and interactive features. Panel (a) shows linked brushing across the global view and the tooltip display when the cursor hovers over an instance. Applied linked brushing, (b), selected points are highlighted in the component spaces and tabularly displayed. Coloring on a statistic (c) highlights structure organized in the attribution space. Interactive tabular display (d) populates when instances are selected. Contribution of the 1D basis effecting the horizontal position (e) parallel coorindate display of the feature attribution from all observations, and horizontal bars show the contribution to the current basis. Regression projection (f) uses the same horizontal projection and fixes the vertical positions to the observed y and residuals, (left and right).}\label{fig:regressioncase}
\end{figure}

>>>>

\caption{Overview of the cheem viewer for regression task highlighting the differences from the classification task and interactive features. Panel (a) PCA of the data and attributions spaces, (b), residual plot, predictions by observed values. Four points areselected points and highlighted in the PC spaces and tabularly displayed. Coloring on a statistic (c) highlights structure organized in the attribution space. Interactive tabular display (d) populates when instances are selected. Contribution of the 1D basis effecting the horizontal position (e) parallel coorindate display of the feature attribution from all observations, and horizontal bars show the contribution to the current basis. Regression projection (f) uses the same horizontal projection and fixes the vertical positions to the observed y and residuals, (left and right).}\label{fig:regressioncase}
\end{figure}
